DCM_investigation

### 2020-10-26 article_figures_ARTHUR_CAPET.Rmd
add light horizons

```{r IntegratedDiagsdf, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
# TOTAL CHL, integration using first linear interpolation on a regular grid, then sum.
if (freshstart){
integrated_diags <- ddply(complete_tmp2, .(juld,platform), summarize,
                          # TOTAL CHL, integration using first linear interpolation on a regular grid, then sum.
                            total_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y, na.rm=T),
                          # chl content relative to MLD depth
                            DoMLD_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y[round(unique(MLD)):200]),
                            UpMLD_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y[  0:round(unique(MLD))]),
                            RaMLD_chla    = UpMLD_chla/total_chla*100,
                          # Visible part based on monthly optical depth
                            optic_depth   = optical_depth[unique(month)]*3,
                            visible_chla  = sum(approx(x=depth, y=fluo,xout = seq(0, optic_depth), rule = 2)$y, na.rm=T), 
                            visible_ratio = visible_chla/total_chla*100, 
                          # Content around DCM 
                            DCMcontent    = try_default(
                              sum(approx(x=depth, y=fluo,xout = seq(round(unique(Zmax)-10), round(unique(Zmax)+10)), rule = 2)$y, na.rm=T),
                              NA, quiet = FALSE), 
                            DCMratio      = DCMcontent/total_chla*100 ,
                          # sigma @ Zdemi 
                          # by definition, sigma @ MLD follows sig surface by a fixed amont. 
                            #sigmaMLD      = sigma[which.min(depth)],
                            ZLow           = min(depth[fluo<0.01]),
                          #  Z90           = depth90b(depth = depth , fluo = fluo,total = total_chla),
                            Z90B           = depth90B(depth = depth , fluo = fluo,total = total_chla, p=0.75),
                            Z90T           = depth90T(depth = depth , fluo = fluo,total = total_chla, p=0.75),
                            sigmalow       = try_default(approx(x=depth, y=sigma, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
                            sigma90B       = try_default(approx(x=depth, y=sigma, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
                            sigma90T       = try_default(approx(x=depth, y=sigma, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
                            sigmaMLD       = min(sigma, na.rm = TRUE),#[which.min(depth)],  !! THIS IS NOT CORRECT !!
                            sigmaMAX       = try_default(approx(x=depth, y=sigma, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
                            sigmaDEMI      = try_default(approx(x=depth, y=sigma, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE), 
                            #Ziso1         = isoPAR(depth = depth , PAR = par),
                            sigmaiso1      = try_default(approx(x=depth, y=sigma, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
                          )
}
```

```{r IntegratedDiagsMerge, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
if (freshstart){
# !!!!! Carefull here, this is much cleaner that the following commented line
# which does not ensure that the order corresponds, only hte number of elements !!!!!!
# Took me a while to track why this was causing different results !! 
tmp_fitc<-merge(tmp_fit ,integrated_diags, by = c('juld','platform'))

tmp_fitc<-merge(tmp_fitc ,integrated_diags_par, by = c('juld','platform'), all.x = TRUE)
#tmp_fit$total_chla_content <- total_chla_content$total_chla

# remove 2014 .. (not enough data) or not.
tmp_fitc   <- tmp_fitc[tmp_fit$year %in% c(2014:2019),]

@@

Density framework shows less spatial variability, and more stable seasonal evolution.

The deepest winter MLD sets pycnal layer of Z_1/2, which remains stable from February to September.
From may to june, a DCM forms and migrate to higher layers.

Unlike the previous plot, the pycnal coordinates allow to dissociate DCM from June to September.
This is indicative of pycnal or mixing forces ruling the location of the DCM, rather than restrictevely light conditions wich tend to be more related to the depth [m] scale.

Obviously nutrient content follows isopycnal layers.
Konovalov (2006) locates the nitrate nitracline at 15.5 kg/m3.

Between August and October, it seems the lower part of CHL limited and Sigma_1/2 rejoins Sigma_max. Light limitation by a well formed DCM ? 
Indeed, it's in August that the percentage of CHL around DCM is highest, so that CHL density in the DCM zone is the thickest. 
**Something strange with MLD .. How many defined MLD in summers ? Is there less ? is that what explain low variability in summer?**
**I changed the definition of sigma MLD above, but ... dont get it.**

```{r sigma}
tmp_sig1 <- subset(tmp_fitco, select = c('month','sigmaMLD','sigmaMAX','sigmalow','sigma90B','sigma90T','sigmaiso1' ,'dcm_or_not','year','shape'))

tmp_sig1$sigmaMAX[tmp_sig1$dcm_or_not==0]<-NA
tmp_sig1$sigmaMAX[tmp_sig1$Zmax>200]<-NA
#tmp_sig1$Zdemi[tmp_sig1$shape %in% c("O","GE","G")]<-NA

@@

@@

```{r paratdcm}
# Attempt to derive PARfraction at the DCM depth

@@

discfig2<-ggplot(tmp_fitcl, aes(x=month, y=PARpartDCM*100)) +
    geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95),
              alpha=0.5,
              color=brewer_pal(palette = MyPal)(2)[2],
              fill=brewer_pal(palette = MyPal)(2)[2])+
  geom_boxplot(aes(group=month), alpha=0.2, notch = TRUE, color=brewer_pal(palette = MyPal)(2)[2],fill=brewer_pal(palette = MyPal)(2)[2])+
  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_y_continuous(breaks = seq(0,5,1), minor_breaks = NULL, limit=c(0,5)) +
  ylab('[% of surface PAR at DCM]')
print(discfig2)

@@

```{r PARatDCM2BIS}
#tmp_fitc<-tmp_fitc[,-which(colnames(tmp_fitc)=="PARpartDCM")]
tmp_fitcl<-merge(tmp_fitc ,integrated_diags_par2, by = c('juld','platform'), all.x = TRUE)

@@

discfigb2
```

```{r discfig}

 gA <- ggplotGrob(discfig1+geom_text(label='a)', x=3.5, y= 1.05, size=5))
 gB <- ggplotGrob(discfig2+geom_text(label='b)', x=3.5, y= 4.8 , size=5 ))

grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

#grid.arrange(discfig1+geom_text(label='a)', x=3.5, y= 1.05)+theme(axis.line.y.left=element_text(margin = margin(t = 20)),#+ylab('')
 #            discfig2+geom_text(label='b)', x=3.5, y= 4.8),#+ylab('')
#             ncol=1)
```
```{r discfigb}

 gA <- ggplotGrob(discfigb1+geom_text(label='a)', x=3.5, y= 1.05, size=5, color='black'))
 gB <- ggplotGrob(discfigb2+geom_text(label='b)', x=3.5, y= 4.8 , size=5, color='black' ))

grid::grid.newpage()
grid::grid.draw(rbind(gA, gB))

#grid.arrange(discfig1+geom_text(label='a)', x=3.5, y= 1.05)+theme(axis.line.y.left=element_text(margin = margin(t = 20)),#+ylab('')
 #            discfig2+geom_text(label='b)', x=3.5, y= 4.8),#+ylab('')
#             ncol=1)
```

```{r ratio_PARatDCM, fig.width=10,fig.height=10, include=FALSE, eval=FALSE}

require(ggmap)
mm <- get_map

mycoord <- c(27,40.5,42,47)
myMap_stamen <- get_map(location=mycoord,source="stamen", maptype="watercolor")
save(myMap_stamen, file="BS_StaMap.Rdata") 
#load(file="BS_StaMap.Rdata")

ms<-ggmap(myMap_stamen, darken = c(0.6,"white"))
ms1<-ms+geom_point(data=subset(tmp_fitc,(month>3)&(month<11)&(!is.na(PARpartDCM))), aes(x=lon,y=lat, color=PARpartDCM*100))+facet_wrap(~month, scale="fixed", ncol=2)+theme_bw()
ms1+scale_color_distiller(palette = 'RdYlBu',limits=c(0,6))

# ms2<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(shape)))+
#   facet_wrap(~month, scale="fixed")+theme_bw()
# ms2#+scale_color_discrete(name="", labels=c('non-DCM','DCM'))

@@

Numerous Spatial analysis have been done without concluding results beyond "Homogeneous behavior across the central basin".

```{r spatial}

require(ggmap)
mm <- get_map

mycoord <- c(27,40.5,42,47)
myMap_stamen <- get_map(location=mycoord,source="stamen", maptype="watercolor")
save(myMap_stamen, file="BS_StaMap.Rdata") 
#load(file="BS_StaMap.Rdata")

ms<-ggmap(myMap_stamen, darken = c(0.6,"white"))
ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)))+facet_wrap(~month, scale="fixed")+theme_bw()
ms1+scale_color_discrete(name="", labels=c('non-DCM','DCM'))

# ms2<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(shape)))+
#   facet_wrap(~month, scale="fixed")+theme_bw()
# ms2#+scale_color_discrete(name="", labels=c('non-DCM','DCM'))

@@

P_years_depth <- ggplot(tmp_zmax, aes(x=month, fill=variable, color=variable)) +
    geom_line(data=tmp_zmaxA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[m]')+theme_bw()+coord_cartesian(ylim=c(90,0), expand = FALSE)+scale_y_reverse()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(.~year)

@@

P_years_sig <-ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_sigA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[kg/m3]')+theme_bw()+coord_cartesian(ylim=c(10,16))+scale_y_reverse()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(.~year)

@@

@@

P_years_part <-ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_partA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,100))+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                     name='part of tot CHL content', labels=c('above MLD',
                                                              'within a 10m band around DCM',
                                                              'above optical depth'))+
  facet_grid(.~year)

@@

@@

P_years_conc <-ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_concA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,4))+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)

@@

```{r, include=FALSE}
tmp_corrC<- dcast(tmp_corr,formula = month~variable, fun.aggregate = mean, na.rm=TRUE)
tmp_corrA<-melt(tmp_corrC, id.vars=c('month'))

P_years_corr <-ggplot(tmp_corr, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_corrA,aes(y=value),alpha =0.5, size=3)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.1))+scale_x_continuous(name='', breaks=c(), labels="")+
  ylab('[-]')+theme_bw()+coord_cartesian(ylim=c(0,4))+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)

P_years_corr
```

```{r, fig.height=15, fig.width=10}
grid.arrange(P_years_depth+theme(legend.position = ''),
             P_years_sig+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()), 
             P_years_part+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()),
             P_years_conc+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()),
             P_years_corr+theme(legend.position = '', strip.background = element_blank(),strip.text.x = element_blank()) ,
             ncol=1)

@@

## Quick interannual Anomalies and correlations 
```{r}
# compute annual anomalies ? 
Zmulti<-ddply(tmp_zmax, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_zmaxA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })
```

```{r}
Smulti<-ddply(tmp_sig, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_sigA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })
```

```{r}
Cmulti<-ddply(tmp_conc, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_concA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })

Pmulti<-ddply(tmp_part, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_partA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })

Xmulti<-ddply(tmp_corr, .(month,year,variable), function(d){
    do<-d
    do$anom = d$value - subset(tmp_corrA, (month==d$month[1]) & (variable==d$variable[1]))[,'value']
    return(do)
   })
```

```{r}
PA_years_depth <- ggplot(Zmulti, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
#  geom_boxplot(aes(y=anom), alpha=.2)+
  ylab('[m]')+theme_bw()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette='Set1')+facet_grid(variable~year, scales = 'free_y')

PA_years_depth
```

```{r}
PA_years_sig <- ggplot(Smulti, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
#  geom_boxplot(aes(y=anom), alpha=.2)+
  ylab('[m]')+theme_bw()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette='Set1')+facet_grid(variable~year, scales = 'free_y')

PA_years_sig
```

```{r}
PA_years_conc <- ggplot(Cmulti, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=anom, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.9))+scale_x_continuous(name='', breaks=c(), labels="")+
#  geom_boxplot(aes(y=anom), alpha=.2)+
  ylab('[m]')+theme_bw()+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+facet_grid(variable~year, scales = 'free_y')

PA_years_conc
```

```{r}
ZmultiCast <-  dcast(Zmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)
ZmultiCastSD <-  dcast(Zmulti,year~variable, value.var = 'anom', fun.aggregate = sd, na.rm=TRUE)
ZmultiCast<-ZmultiCast[,-which(colnames(ZmultiCast)=='Zdemi')]

SmultiCast <-  dcast(Smulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

PmultiCast <-  dcast(Pmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

CmultiCast <-  dcast(Cmulti,year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

pdt <- merge(ZmultiCast,SmultiCast,by = c('year'))
pdt <- merge(pdt,PmultiCast,by = c('year'))
pdt <- merge(pdt,CmultiCast,by = c('year'))

require(GGally)
ggpairs(pdt,columns = 3:11 )+theme_bw()
```

```{r}
ggcorr(pdt, method = c("everything", "spearman"), geom = 'circle')
```

```{r}
ZmultiCastM   <-  dcast(Zmulti,year+month~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

ZmultiCastMSD <-  dcast(Zmulti,year+month~variable, value.var = 'anom',
                        fun.aggregate = sd, na.rm=TRUE)
ZmultiCastM   <-      ZmultiCastM[,-which(colnames(ZmultiCastM)=='Zdemi')]

SmultiCastM <-  dcast(Smulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

PmultiCastM <-  dcast(Pmulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

CmultiCastM <-  dcast(Cmulti,month+year~variable, value.var = 'anom', fun.aggregate = mean, na.rm=TRUE)

pdtM <- merge(ZmultiCastM,SmultiCastM,by = c('year','month'))
pdtM <- merge(pdtM,PmultiCastM,by = c('year','month'))
pdtM <- merge(pdtM,CmultiCastM,by = c('year','month'))

ggpairs(pdtM,columns = c(3,4,5,9,10,14,16,17,18) )+theme_bw()
```

```{r}
ggcorr(pdtM, method = c("pairwise.complete.obs", "spearman"), geom = 'circle')

```{r}
ggplot(pdt,aes(x=Z90B, y=Zmax, color=factor(year)))+
  geom_point(size=4)+
  geom_point(data=pdtM)+theme_bw()
```

>>>>

```{r add light data to full data}
interpolated_light_data <- ldply(as.list(unique(complete_tmp2$juld)), function(i){
  tmp1 <- complete_tmp2[complete_tmp2$juld == i,]
  tmp2 <- initPAR[initPAR$juld == i,]
  if(nrow(tmp2) == 0){
    absolute_light <- rep(NA, nrow(tmp1))
    # relative % of incoming surface PAR
    relative_light <- absolute_light
  }else{
    absolute_light <- approx(tmp2$depth, tmp2$par, tmp1$depth)$y
    # compute relative % of incoming surface PAR
    relative_light <- (absolute_light/tmp2$par[1])*100 # could also put max(tmp2$par) car surface = max_par, therefore no ordering issue will appear (but tmp2$par[1] is good) 
  }
  data.frame(depth = tmp1$depth, absolute_light = absolute_light, relative_light = relative_light)
})

# add it to complete_tmp2
complete_tmp2 <- cbind(complete_tmp2, light = interpolated_light_data$relative_light, light_absolute = interpolated_light_data$absolute_light)

```{r IntegratedDiagsdf, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
# TOTAL CHL, integration using first linear interpolation on a regular grid, then sum.
if (freshstart){
integrated_diags <- ddply(complete_tmp2, .(juld,platform), summarize,
                          # TOTAL CHL, integration using first linear interpolation on a regular grid, then sum.
                            total_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y, na.rm=T),
                          # chl content relative to MLD depth
                            DoMLD_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y[round(unique(MLD)):200]),
                            UpMLD_chla    = sum(approx(x=depth, y=fluo,xout = seq(0,200), rule = 2)$y[  0:round(unique(MLD))]),
                            RaMLD_chla    = UpMLD_chla/total_chla*100,
                          # Visible part based on monthly optical depth
                            optic_depth   = optical_depth[unique(month)]*3,
                            visible_chla  = sum(approx(x=depth, y=fluo,xout = seq(0, optic_depth), rule = 2)$y, na.rm=T), 
                            visible_ratio = visible_chla/total_chla*100, 
                          # Content around DCM 
                            DCMcontent    = try_default(
                              sum(approx(x=depth, y=fluo,xout = seq(round(unique(Zmax)-10), round(unique(Zmax)+10)), rule = 2)$y, na.rm=T),
                              NA, quiet = FALSE), 
                            DCMratio      = DCMcontent/total_chla*100 ,
                          # sigma @ Zdemi 
                          # by definition, sigma @ MLD follows sig surface by a fixed amont. 
                            #sigmaMLD      = sigma[which.min(depth)],
                            ZLow           = min(depth[fluo<0.01]),
                          #  Z90           = depth90b(depth = depth , fluo = fluo,total = total_chla),
                            Z90B           = depth90B(depth = depth , fluo = fluo,total = total_chla, p=0.75),
                            Z90T           = depth90T(depth = depth , fluo = fluo,total = total_chla, p=0.75),
                            sigmalow       = try_default(approx(x=depth, y=sigma, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
                            sigma90B       = try_default(approx(x=depth, y=sigma, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
                            sigma90T       = try_default(approx(x=depth, y=sigma, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
                            sigmaMLD       = min(sigma, na.rm = TRUE),#[which.min(depth)],  !! THIS IS NOT CORRECT !!
                            sigmaMAX       = try_default(approx(x=depth, y=sigma, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
                            sigmaDEMI      = try_default(approx(x=depth, y=sigma, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE), 
                            #Ziso1         = isoPAR(depth = depth , PAR = par),
                            sigmaiso1      = try_default(approx(x=depth, y=sigma, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE),
                          ### 
                          # Adding diags for LIGHT Horizon here
                            ISOlow       = try_default(approx(x=depth, y=light, xout=ZLow, rule=2)$y,NA, quiet = FALSE),
                            ISO90B       = try_default(approx(x=depth, y=light, xout=Z90B, rule=2)$y,NA, quiet = FALSE),
                            ISO90T       = try_default(approx(x=depth, y=light, xout=Z90T, rule=2)$y,NA, quiet = FALSE),
                            ISOMLD       = min(light, na.rm = TRUE),
                            ISOMAX       = try_default(approx(x=depth, y=light, xout=unique(Zmax), rule=2)$y,NA, quiet = FALSE),
                            ISODEMI      = try_default(approx(x=depth, y=light, xout=unique(Zdemi), rule=2)$y,NA, quiet = FALSE),
                          # just to see
                            ISO_iso1 = try_default(approx(x=depth, y=light, xout=unique(Ziso1b), rule=2)$y,NA, quiet = FALSE)
                          )
}

```{r IntegratedDiagsMerge, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
if (freshstart){
tmp_fitc<-merge(tmp_fit ,integrated_diags, by = c('juld','platform'))

tmp_fitc<-merge(tmp_fitc ,integrated_diags_par, by = c('juld','platform'), all.x = TRUE)

tmp_fitc   <- tmp_fitc[tmp_fit$year %in% c(2014:2019),]

@@

```{r Fig6}
tmp_sig1 <- subset(tmp_fitco, select = c('month','sigmaMLD','sigmaMAX','sigmalow','sigma90B','sigma90T','sigmaiso1' ,'dcm_or_not','year','shape'))

tmp_sig1$ISOMAX[tmp_sig1$dcm_or_not==0]<-NA
tmp_sig1$ISOMAX[tmp_sig1$Zmax>200]<-NA

@@

## Absolute light Horizons

```{r Review Fig light}

tmp_iso1 <- subset(tmp_fitco, select = c('month','ISOMLD','ISOMAX','ISOlow','ISO90B','ISO90T','ISO_iso1' ,'dcm_or_not','year','shape'))

tmp_iso1$sigmaMAX[tmp_iso1$dcm_or_not==0]<-NA
tmp_iso1$sigmaMAX[tmp_iso1$Zmax>200]<-NA

tmp_iso <- melt(tmp_iso1[,-which(colnames(tmp_iso1)=='dcm_or_not')], id.vars=c('month','year','shape'))

ggplot(tmp_iso, aes(x=month, fill=variable, color=variable)) +
    geom_smooth(aes(y=value),stat = 'summary',
#              fun.data = median_hilow,
              fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), alpha=0.5)+
  geom_boxplot(aes(y=value, group=interaction(month,variable)), alpha=0.2, notch = TRUE)+
        scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  #scale_y_continuous(trans = 'log10') + ylab('[microMoleQuanta/m^2/sec]') +
  ylab('% of Incoming PAR') + theme_bw()  + scale_y_continuous(trans = 'log10') +
      scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="ISO Horizons", 
                       labels=list(TeX('$\\ISO_{MLD}$'),
                                TeX('$\\ISO_{DCM}$'),
                                TeX('$\\ISO_{low}$'),
                                TeX('$\\ISO_{50,bottom}$'),
                                TeX('$\\ISO_{50,top}$'),
                                TeX('$\\ISO_{\\mathrm{PAR}\\,1%}$')))

@@

```{r paratdcm, error=FALSE, warning=FALSE, echo=FALSE, message=FALSE, results='hide', include=FALSE, eval=TRUE}
# Attempt to derive PARfraction at the DCM depth

@@

discfig2<-ggplot(tmp_fitcl, aes(x=month, y=PARpartDCM*100)) +
    geom_smooth(stat = 'summary',
#              fun.data = median_hilow,
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95),
              alpha=0.5,
              color=brewer_pal(palette = MyPal)(2)[2],
              fill=brewer_pal(palette = MyPal)(2)[2])+
  geom_boxplot(aes(group=month), alpha=0.2, notch = TRUE, color=brewer_pal(palette = MyPal)(2)[2],fill=brewer_pal(palette = MyPal)(2)[2])+
  theme_bw()+scale_x_continuous(NULL, labels = month.abb, breaks = seq(1,12))+
  scale_y_continuous(breaks = seq(0,5,1), minor_breaks = NULL, limit=c(0,5)) +
  ylab('[% of surface PAR at DCM]')
#print(discfig2)

@@

```{r PARatDCM2BIS, error=FALSE}
#tmp_fitc<-tmp_fitc[,-which(colnames(tmp_fitc)=="PARpartDCM")]
tmp_fitcl<-merge(tmp_fitc ,integrated_diags_par2, by = c('juld','platform'), all.x = TRUE)

@@

print(discfigb2)
```

@@

```{r Fig4,fig.width=8,fig.height=8}

require(ggmap)
#mm <- get_map

mycoord <- c(27,40.5,42,47)
myMap_stamen <- get_map(location=mycoord,source="stamen",maptype = "watercolor", force = TRUE)

tmp_fitco$monthn<-factor(tmp_fitco$month, labels = month.abb[unique(tmp_fitco$month)])

ms<-ggmap(myMap_stamen)
ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)))+
  facet_wrap(~monthn, scale="fixed")+
  theme_bw()+
  scale_color_discrete(name="", labels=c('non-DCM','DCM'))+
  theme(legend.position = 'top', legend.box = "horizontal")+
  scale_x_continuous(name='', breaks = c(27,30,33,36,39), limits = c(27,42), expand = expand_scale(add = 0))+
  scale_y_continuous(name='', breaks = seq(41,47), limits = c(40.7,47), expand = expand_scale(add = 0))

ms1
```

@@

#levels(tmp_zmax$variable)<-levels(tmp_zmax$variable)[-which()]
#levels(tmp_zmaxA$variable)<-levels(tmp_zmax$variable)[-7]

P_years_depth <- ggplot(subset(tmp_zmax, variable !="Zdemi"), aes(x=month, fill=variable, color=variable)) +
    geom_line(data=subset(tmp_zmaxA, variable !="Zdemi"),aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=variable),
                  stat = 'summary',
                  fun.data = mean_cl_boot,
                  fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab('[m]')+theme_bw()+
  coord_cartesian(ylim=c(90,0), expand = FALSE)+scale_y_reverse()+
  scale_color_brewer(aesthetics = c("colour", "fill"),
                       type = qual ,
                       palette=MyPal,
                       name="Depth Horizons", 
                       labels=list(TeX('$z_{MLD}$'),
                                TeX('$z_{DCM}$'),
                                TeX('$z_{low}$'),
                                TeX('$z_{50,bottom}$'),
                                TeX('$z_{50,top}$'),
                                TeX('$z_{\\mathrm{PAR}\\,1%}$')))+
#  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal, name='')+
  facet_grid(.~year)+
  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
  guides(colour = guide_legend(nrow = 1))

@@

P_years_sig <-ggplot(tmp_sig, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_sigA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab('[kg/m3]')+theme_bw()+
  coord_cartesian(ylim=c(10,16), expand = FALSE)+
  scale_y_reverse()+
  #scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal,
                       name="Density Horizons", 
                       labels=list(TeX('$\\sigma_{MLD}$'),
                                TeX('$\\sigma_{DCM}$'),
                                TeX('$\\sigma_{low}$'),
                                TeX('$\\sigma_{50,bottom}$'),
                                TeX('$\\sigma_{50,top}$'),
                                TeX('$\\sigma_{\\mathrm{PAR}\\,1%}$')))+
  facet_grid(.~year)+
  theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+
          guides(colour = guide_legend(nrow = 1))

@@

```{r inter_parts, include=FALSE}

@@

P_years_part <-ggplot(tmp_part, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_partA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args =  list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab('[%]')+theme_bw()+coord_cartesian(ylim=c(0,100), expand = FALSE)+
  scale_color_brewer(name='Part of tot. Chl:',
                     labels=c('above MLD','within 5m of DCM','above optical depth'),
                     aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))

@@

```{r inter_conc, include=FALSE}

@@

P_years_conc <-ggplot(tmp_conc, aes(x=month, fill=variable, color=variable)) +
       geom_line(data=tmp_concA,aes(y=value),alpha =1, size=0.5, linetype=2)+
      geom_smooth(aes(y=value, group=interaction(year, variable)),stat = 'summary',
             fun.data = mean_cl_boot,
              fun.args = list(conf.int = 0.95), 
                  alpha=0.2, linetype=0)+
  scale_x_continuous(name='', breaks=c(), labels="", limits=c(.5,12.5))+
  ylab('[mg/m3]')+theme_bw()+coord_cartesian(ylim=c(0,3), expand = FALSE)+
  scale_color_brewer(aesthetics = c("colour", "fill"),type = qual ,palette=MyPal)+
  facet_grid(.~year)+scale_color_brewer(aesthetics = c("colour", "fill"),type = qual,
                       palette=MyPal, 
                       name="Chla concentrations",
                       labels=c("Average","Surface","DCM"))+
  facet_grid(.~year)+theme(legend.position = 'top', legend.box = "horizontal",panel.spacing = unit(0, "lines"))+ guides(colour = guide_legend(nrow = 1))

@@

```{r Fig11, fig.height=12, fig.width=10}
grid.arrange(P_years_depth,
             P_years_sig+theme( strip.background = element_blank(),strip.text.x = element_blank()), 
             P_years_part+theme( strip.background = element_blank(),strip.text.x = element_blank()),
             P_years_conc+theme( strip.background = element_blank(),strip.text.x = element_blank()),
             ncol=1)

@@
